%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CURRICULUM 
% Tipologia documento
\documentclass{DFCV}
\usepackage[english]{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GENERAL INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}{\textwidth}
	\begin{minipage}[c]{.6\textwidth}
		Robotics and Perception Group \\
		Department of Informatics \\
		University of Zurich \\
		Andreasstrasse 15, Office 2.18\\
	    8050 Zurich, Switzerland
	\end{minipage}
	\begin{minipage}[b]{.4\textwidth}
	    \flushleft
	                email: \texttt{\href{mailto:falanga@ifi.uzh.ch}{falanga@ifi.uzh.ch}} \\
		            phone: +41 44 635 45 75 \\
		            mobile: +41 79 473 26 69
		            %web: \texttt{\href{http://www.davidefalanga.com}{www.davidefalanga.com}}
	\end{minipage}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTERESTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsectiontitle{Research Interests}
	\cvelement{}{}{}{Dynamical Systems, Control Theory, Robotics.}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CURRENT POSITION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsectiontitle{Current Position}
	\cvelement{Research Assistant}
			  {04/2015 - Today}
			  {Robotics and Perception Group | University of Zurich, Switzerland}
			  {Research Assistant at the Robotics and Perception Group (http://rpg.ifi.uzh.ch) under the supervision of Prof. Davide Scaramuzza.}
		  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PAST POSITION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsectiontitle{Past Positions}	  
	\cvelement{Project Assistant}
	          {11/2014 - 03/2015}
	          {Swisslog | Buchs AG, Switzerland}
	          {Development of an autonomous manipulation system able to pick items from a chaotic bin using 2D/3D vision without relying on CAD models.}
		  		      
	\cvelement{Student Intern}
			  {04/2014 - 10/2014}
			  {PRISMA Lab | University of Naples ``Federico II", Italy}
			  {Development and implementation of nonlinear control laws to stabilize a disk free to roll upon another controlled disk, both in simulation and on a real setup.}
				   
	\cvelement{Web-journalist}
			  {11/2007 - 04/2014}
			  {GruppoHTML.it | Rome, Italy}
			  {Over 3000 among news, tutorials, in-depth articles and reviews published at WebNews.it, Download.HTML.it and HTML.it/Linux.}
		   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsectiontitle{Education}
	\cvelement{M.Sc.}
		      {03/2015}
	   	      {University of Naples ``Federico II", Italy}
		      {Master degree (Laurea Magistrale) in Automation Engineering, major in Robotics and Control. Thesis concerning dynamic nonprehensile manipulation in the case of a free disk rolling on an actuated disk. \emph{Summa cum laude}.}
	
	\cvelement{B.Sc.}
		      {09/2012}
		      {University of Naples ``Federico II", Italy}
		      {Bachelor degree (Laurea Triennale) in Automation Engineering, Major in Dynamic Systems and Control. Thesis concerning fault detection in discrete event systems using Petri nets. }
		   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsectiontitle{Skills}
	\cvelement{Scientific skills}{}{}
		      {\begin{itemize} [noitemsep]
		      		\item Dynamical Systems: analysis, identification, state estimation, (non)linear control 
		      		\item Robotics: mobile robots, manipulators, path planning, machine vision
		       \end{itemize}
		       }
	\cvelement{Technical skills}{}{}
		      {\begin{itemize} [noitemsep]
		      		\item Programming: C/C++, Java, Matlab, ROS, HTML/CSS, Bash
		      		\item Operating Systems: OS X, Linux, Windows
		      		\item Simulation: Simulink, V-REP
		      	\end{itemize}
		      	}
	\cvelement{Languages}{}{}
			  {Italian (mothertongue), English (very good)}
\end{document}